\begin{innerlist}

  \item[] \textbf{PI},
  ``Efficient Data Reduction via Active Learning Augmented Coresets'',,
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0003266
    \item[-] \$1,000,000/yr.
    \item[-] FY 25-27.
  \end{innerlist}

  \item[] \textbf{Co-I},
  ``Scalable Physics-Constrained Emulation of Stochastic Moments of Quantum Processing Units'',
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0003300
    \item[-] \$500,000/yr.
    \item[-] FY 25-26.
  \end{innerlist}

  \item[] \textbf{Co-I},
  ``Science with LSST Year 1 Data'',
  \begin{innerlist}
    \item[-] LLNL LDRD ER
    \item[-] \$1,000,000/yr.
    \item[-] FY 25-27.
  \end{innerlist}

  \item[] \textbf{Co-I},
  ``Decentralized Strategic Decision Making via Linearly Solvable Markov Games'',
  \begin{innerlist}
    \item[-] LLNL LDRD ER
    \item[-] \$600,000/yr.
    \item[-] FY 25-27.
  \end{innerlist}

  \item[] \textbf{Co-I},
  ``Uncertainty-Aware Realtime Algorithmic Calibration in Distributed Computing Environments'',
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0003266
    \item[-] \$1,200,000/yr.
    \item[-] FY 24-27.
  \end{innerlist}

  \item[] \textbf{PI},
  ``Scalable and Highly Concurrent Sampling Algorithms for Scale-Free Graphs'',
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0002722
    \item[-] \$800,000/yr.
    \item[-] FY 23-25.
  \end{innerlist}

  \item[] \textbf{Co-I},
  ``Probabilistic AI Pipeline Modules for Rubin LSST Dark Energy'',
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0002705
    \item[-] \$1,000,000/yr.
    \item[-] FY 23-25.
  \end{innerlist}

  \item[] \textbf{Co-PI},
  ``Scalable Single-Pass Compressive Autoencoders'',
  \begin{innerlist}
    \item[-] LLNL LDRD Feasibility Study
    \item[-] \$150,000/yr.
    \item[-] FY 23.
  \end{innerlist}

  \item[] \textbf{Co-I},
  ``EpochGrafts: Relational Data Fusion via Dynamic Graph Analysis'',
  \begin{innerlist}
    \item[-] LLNL LDRD ER
    \item[-] \$500,000/yr.
    \item[-] FY 22-24.
  \end{innerlist}

  \item[] \textbf{PI},
  ``Scalable Non-stationary Approximate Gaussian Processes'',
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0002493
    \item[-] \$800,000/yr.
    \item[-] FY 22-24.
  \end{innerlist}

  \item[] \textbf{PI},
  ``Distributed Memory Sketching Algorithms at HPC Scales'',
  \begin{innerlist}
    \item[-] DOE ASCR DE-FOA-0002497
    \item[-] \$400,000/yr.
    \item[-] FY 22-23.
  \end{innerlist}

  \item[] \textbf{PI},
  ``\texttt{croquis}: Distributed Subspace Embeddings for High Performance Computing'',
  \begin{innerlist}
    \item[-] LLNL ISCP Tech Base
    \item[-] \$100,000/yr.
    \item[-] FY 21-22.
  \end{innerlist}

\end{innerlist}
