\begin{innerlist}

  \item[] \textbf{Juliette Mukangango},
  PhD student in Statistics,
  Colorado School of Mines.
  Novel loss and objective functions for outlier robustness in training sparse
  MuyGPs models.
  Primary Advisor: Douglas Nychka.
  Summer 2023.

  \item[] \textbf{Akil Andrews},
  PhD student in Computer Science,
  University of New Mexico.
  Adaptive Bayesian optimization under changing data representations.
  Primary Advisor: Melanie E Moses.
  Summer 2023.

  \item[] \textbf{Ian McGovern},
  PhD student in Statistics,
  University of California, Los Angeles.
  Uncertainty analysis of hybrid deep neural network and Gaussian process
  predictions.
  Primary Advisor: Frederic Schoenberg.
  Summer 2023.

  \item[] \textbf{Abiodun Sumonu},
  PhD student in Mathematics,
  University of Alabama.
  Survey of Biclustering Algorithms.
  Summer 2023.

  \item[] \textbf{Keegan Kresge},
  Post Baccalaureate in Mathematics,
  DOD.
  K-Nearest Neighbors performance of exponentiated subspace embeddings on large
  graphs.
  Summer 2023.

  \item[] \textbf{Marina Dunn},
  Masters student in Data Science,
  University of California, Riverside.
  Visualizing sparse Gaussian process optimization.
  Summer 2022.

  \item[] \textbf{Killian Wood},
  PhD Student in Applied Mathematics,
  University of Colorado, Boulder.
  Multiscale Bayesian optimization of MuyGPs.
  Primary Advisor: Emiliano Dall'Anese.
  Summer 2022.

  \item[] \textbf{Micha{\l}
    Lisicki},
  PhD student in Computer Science,
  University of Guelph.
  Distributional reinforcement learning on gridworld environments.
  Primary Advisor: Graham Taylor.
  Summer 2022.

  \item[] \textbf{Sudharshan Srinivasan},
  PhD student in Computer Science,
  University of Oregon.
  Communication optimization for highly non-uniform distributed graph algorithms.
  Primary Advisor: Boyana Norris.
  Summer 2021.

  \item[] \textbf{Alec Dunton},
  PhD student in Applied Mathematics,
  University of Colorado, Boulder.
  Parameter sensitivity of stochastic block models under subspace embeddings.
  Primary Advisor: Alireza Doostan.
  Summer 2020.

\end{innerlist}
