\begin{innerlist}

  \item[] \textbf{Edem Boahen},
  PhD student in Mathematics.
  \begin{innerlist}
    \item[-] Michigan State University.
    \item[-] Clustering guarantees for power iteration algorithms on degree-corrected
      stochastic block models.
    \item[-] Primary Advisor: Mark Iwen.
    \item[-] Summer 2024-present.
  \end{innerlist}
  
  \item[] \textbf{Sunanda Thirunabukkarasu (Mila Arasu)},
  BS student in Astrophysics.
  \begin{innerlist}
    \item[-] Arizona State University.
    \item[-] Simulating cosmic lensing shear with realistic B- and E-mode shifts.
    \item[-] Summer 2024.
  \end{innerlist}

  \item[] \textbf{Lance Fletcher},
  PhD student in Computer Science.
  \begin{innerlist}
    \item[-] Texas A \& M University.
    \item[-] Massively parallel random walk sampling and embeddings.
    \item[-] Primary Advisor: Roger Pearce.
    \item[-] Autumn 2023-present.
  \end{innerlist}

  \item[] \textbf{Juliette Mukangango},
  PhD student in Statistics.
  \begin{innerlist}
    \item[-] Colorado School of Mines.
    \item[-] Novel loss and objective functions for outlier robustness in training sparse MuyGPs models.
    \item[-] Primary Advisor: Douglas Nychka.
    \item[-] Summer 2023.
  \end{innerlist}

  \item[] \textbf{Akil Andrews},
  PhD student in Computer Science.
  \begin{innerlist}
    \item[-] University of New Mexico.
    \item[-] Adaptive Bayesian optimization under changing data representations.
    \item[-] Primary Advisor: Melanie E Moses.
    \item[-] Summer 2023.
  \end{innerlist}

  \item[] \textbf{Ian McGovern},
  PhD student in Statistics.
  \begin{innerlist}
    \item[-] University of California, Los Angeles.
    \item[-] Uncertainty analysis of hybrid deep neural network and Gaussian process predictions.
    \item[-] Primary Advisor: Frederic Schoenberg.
    \item[-] Summer 2023.
  \end{innerlist}

  \item[] \textbf{Abiodun Sumonu},
  PhD student in Mathematics.
  \begin{innerlist}
    \item[-] University of Alabama.
    \item[-] Survey of Biclustering Algorithms.
    \item[-] Summer 2023.
  \end{innerlist}

  \item[] \textbf{Marina Dunn},
  Masters student in Data Science,
  \begin{innerlist}
    \item[-] University of California, Riverside.
    \item[-] Visualizing sparse Gaussian process optimization.
    \item[-] Summer 2022.
  \end{innerlist}

  \item[] \textbf{Killian Wood},
  PhD Student in Applied Mathematics.
  \begin{innerlist}
    \item[-] University of Colorado, Boulder.
    \item[-] Multiscale Bayesian optimization of MuyGPs.
    \item[-] Primary Advisor: Emiliano Dall'Anese.
    \item[-] Summer 2022.
  \end{innerlist}

  \item[] \textbf{Micha{\l}
    Lisicki},
  PhD student in Computer Science.
  \begin{innerlist}
    \item[-] University of Guelph.
    \item[-] Distributional reinforcement learning on gridworld environments.
    \item[-] Primary Advisor: Graham Taylor.
    \item[-] Summer 2022.
  \end{innerlist}

  \item[] \textbf{Sudharshan Srinivasan},
  PhD student in Computer Science.
  \begin{innerlist}
    \item[-] University of Oregon.
    \item[-] Communication optimization for highly non-uniform distributed graph algorithms.
    \item[-] Primary Advisor: Boyana Norris.
    \item[-] Summer 2021.
  \end{innerlist}

  \item[] \textbf{Alec Dunton},
  PhD student in Applied Mathematics.
  \begin{innerlist}
    \item[-] University of Colorado, Boulder.
    \item[-] Parameter sensitivity of stochastic block models under subspace embeddings.
    \item[-] Primary Advisor: Alireza Doostan.
    \item[-] Summer 2020.
  \end{innerlist}

\end{innerlist}
