\item \textbf{Ben W. Priest}, Era Vuksani, Neal Wagner, Brady Tello, Kevin M. Carter, and William W. Streilein. 
	Agent-based simulation in support of moving target cyber defense technology development and evaluation.
	In \emph{Proceedings of the 18th Symposium on Communications \& Networking, 2015 ACM Spring Simulation Multi-Conference}, 
	CNS/SpringSim. 
	2015.

\item Kevin M. Carter, Ramona S. Caceres and \textbf{Ben Priest}.
	Characterization of latent social networks discovered through computer network logs.
	In \emph{Networks in the Social and Information Sciences workshop of the 29th Annual Conference on Neural Information Processing Systems},
	NIPS.
	2015.

\item \textbf{Ben Priest} and Kevin M. Carter.
	Characterizing latent user interests on enterprise networks.
	In \emph{Proceedings of the Twenty-Seventh International Florida Artificial Intelligence Research Society Conference}, 
	FLAIRS. 
	2014.

\item Kevin M. Carter, Rajmonda S. Caceres, and \textbf{Ben Priest}.
	Latent community discovery through enterprise user search query modeling.
	In \emph{Proceedings of the 37th International ACM SIGIR Conference on Research \& Development in Information Retrieval}, 
	SIGIR. 
	2014.

\item Kevin Gold, Zachary J. Weber, \textbf{Ben Priest}, Josh Ziegler, Karen Sittig, William W. Streilein, and Mark Mazumder.
	Modeling how thinking about the past and future impacts network traffic with the GOSMR architecture.
	In \emph{International conference on Autonomous Agents and Multi-Agent Systems}, 
	AAMAS. 
	2013.

\item \textbf{Ben Priest} and Kevin Gold.
	Utility discounting explains informational website traffic patterns before a hurricane.
	In \emph{Proceedings of the 22nd International World Wide Web Conference}, 
	WWW. 
	2013.

\item Kevin Gold, \textbf{Ben Priest}, and Kevin M. Carter
	An expectation maximization approach to detecting compromised remote access accounts.
	In \emph{Proceedings of the Twenty-Sixth International Florida Artificial Intelligence Research Society Conference}, 
	FLAIRS. 
	2013.