\item Trevor Steil, Tahsin Reza, Keita Iwabuchi, \textbf{Benjamin W. Priest}, Geoff Sanders, and Roger Pearce.
	Tripoll: Computing Surveys of Triangles in Massive-Scale Temporal Graphs with Metadata.
	In \emph{Proceedings of the International Conference for High Performance Computing, Networking, Storage and Analysis},
	SC. 
	2021.
	arXiv:2107.12330.

\item Im\`ene R. Goumiri, Amanda L. Muyskens, Michael D. Schneider, \textbf{Benjamin W. Priest}, and Robert E. Armstrong.
	Star-Galaxy Separation via Gaussian Prcesses with Model Reduction.
	In \emph{Proceedings of the Advanced Maui Optical and Space Surveillance Technologies Conference},
	AMOS.
	2020.
	arXiv:2010.06094.

\item \textbf{Benjamin W. Priest}, Alec Dunton, and Geoffrey Sanders.
	Scaling Graph Clustering with Distributed Sketches.
	In \emph{Proceedings of the IEEE High Performance Extreme Computing Conference}, 
	HPEC. 
	\textbf{Graph Challenge Champion}.
	2020.
	arXiv:2007.12669.

\item Im\'{e}ne R. Goumiri, \textbf{Benjamin W. Priest}, and Michael D. Schneider.
	Reinforcement Learning via Gaussian Processes with Neural Network Dual Kernels.
	In 2020 IEEE Conference on Games.
	CoG.
	2020.
	arXiv:2004.05198.

\item Trevor Steil, Scott McMillan, Geoffrey Sanders, Roger Pearce, and \textbf{Benjamin W. Priest}.
	Kronecker Graph Generation with Ground Truth for 4-Cycles and Dense Structure in Bipartite Graphs.
	In \emph{2020 IEEE International Parallel and Distributed Processing Symposium Workshops}, 
	IPDPSW. 
	2020.

\item Roger Pearce, Trevor Steil, \textbf{Benjamin W. Priest}, and Geoffrey Sanders.
	One Quadrillion Triangles Queried on One Million Processors.
	In \emph{Proceedings of the IEEE High Performance Extreme Computing Conference}, 
	HPEC. 
	\textbf{Graph Challenge Champion}.
	2019.

\item \textbf{Benjamin W. Priest}, Trevor Steil, Geoffrey Sanders, and Roger Pearce.
	You've {G}ot {M}ail (YGM): Building missing asynchronous communication primitives.
	In \emph{2019 IEEE International Parallel and Distributed Processing Symposium Workshops}, 
	IPDPSW. 
	2019.

\item Trevor Steil, \textbf{Benjamin W. Priest}, Geoffrey Sanders, Roger Pearce, Timothy La Fond, and Keita Iwabuchi.
	Distributed Kronecker graph generation with ground truth of many graph properties.
	In \emph{2019 IEEE International Parallel and Distributed Processing Symposium Workshops}, 
	IPDPSW. 
	2019.

\item \textbf{Benjamin W. Priest}, Roger Pearce, and Geoffrey Sanders.
	Estimating edge-local triangle count heavy hitters in edge-linear time and almost-vertex-linear space.
	In \emph{Proceedings of the IEEE High Performance Extreme Computing Conference}, 
	HPEC. 
	2018.

\item Luan Hoy Pham, Massimiliano Albanese, and \textbf{Benjamin W. Priest}.
	A quantitative framework to model advanced persistent threats.
	In \emph{Proceedings of the 15th International Conference on Security and Cryptography}, 
	SECRYPT. 
	\textbf{Best Paper Award}.
	2018.
